COG-ED Manuscript

### 2021-12-10 06_Paper/COG-ED/Manuscript.Rmd
wrote h2b analysis

We aim to conduct all analysis as described in Westbrook et al. [-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations regarding data cleaning and degrees of freedom. The performance measure *d'* will be computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990]. Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 100 ms, as the relevant cognitive processes cannot have been completed before [@Whelan2008; @Berger2021]. Error- and post-error trials will be excluded, because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
Declining performance will be investigated by calculating a repeated measures analysis of variance (rmANOVA) with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
Another rmANOVA with three paired contrasts will be computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
For each ED round, SVs will be calculated by adding or subtracting 0.015625 from the last monetary value of the flexible level, depending on the participant's last choice.
Then, these final monetary values will be divided by 2€, and the SV of each level per participant will be computed by averaging all final values of each level, regardless of whether it was fixed or flexible.
A rmANOVA with six paired contrasts will be computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
Tukey method will be used for the paired contrasts of each rmANOVA, including *p*-value adjustment.

To determine the influence of task performance in the association of SVs and n-back level, we will set up a multi-level model.
+ NFC
**MLM explanation goes here**

fit using $lmerTest$ package
# center level 1 predictors
 two ways: centering at the grand mean (CGM) vs. centering within cluster (CWC) = group mean centering
 level 1 predictor (SV) is of substantive interest
 CWC
# level 2 predictor
 CGM
null model > ICC
random slopes model
  controlled for performance (d', RT), correct and post-correct trials
parameter estimation REML
include model?
simple slopes analysis

@@

  library(interactions)
  m1_h2b.ss <- sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none", 
                    cond.int = T,                                       # print conditional intercepts
                    johnson_neyman = T, jnplot = T, control.fdr = T)    # calculate Johnson Neyman intervals, 
                                                                        # create plot, adjust false discovery rate

@@

  # TODO: Corinna go on here :) 
    # -> prepare tables: MLM results + huxtable
    # -> write methods
    # -> write results

    # "SVs decline stronger with increasing load level for individuals with low compared to high NFC scores"

>>>>

We aim to conduct all analysis as described in Westbrook et al. [-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations regarding data cleaning and degrees of freedom. The performance measure *d'* will be computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990]. Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 100 ms, as the relevant cognitive processes cannot have been completed before [@Whelan2008; @Berger2021]. Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in multi-level-model (MLM), because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
To test our hypotheses, we perform a series of rmANOVAs and MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results [@Singmann2017]. 
Declining performance will be investigated by calculating a rmANOVA with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
Another rmANOVA with three paired contrasts will be computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
For each ED round, SVs will be calculated by adding or subtracting 0.015625 from the last monetary value of the flexible level, depending on the participant's last choice.
Then, these final monetary values will be divided by 2€, and the SV of each level per participant will be computed by averaging all final values of each level, regardless of whether it was fixed or flexible.
A rmANOVA with six paired contrasts will be computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
Tukey method will be used for the paired contrasts of each rmANOVA, including *p*-value adjustment.

To determine the influence of task performance in the association of SVs and n-back level, we will set up a MLM using the $lmerTest$ package. 
We apply restricted maximum likelihood (REML) to fit the model.
First, we calculate the intraclass correlation (ICC) on the basis of the null model.
Second, we estimate a random slopes model of SV including n-back load level as level-1-predictor and, additionally, NFC as level-2-predictor. 
Within the model, we control for *d'*, RT, correct and post-correct trials.
$$
SV \sim level\ * NFC + d' + RT + correct + postcorrect + (level|subject)
$$
Level-1-predictors are centered within cluster, whereas the level-2-predictor is centered at the grand mean as recommended by Enders & Tofighi [-@Enders2007].
Third, we perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
# TODO: Johnson-Neyman plot

@@

  library(interactions)
  m1_h2b.ss <- sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none", 
                    cond.int = T,                                       # print conditional intercepts
                    johnson_neyman = T, jnplot = T, control.fdr = T)    # calculate Johnson Neyman intervals,

@@
